---
title: Instagram reel logging
author: Amelie Prentice (apre620)
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## What's going on with this data?

I am trying to analyse the data of the first reel that I see each time I open instagram.

Below we have three different graphs. The first bar graph shows the count of different categories of reels I see when I open Instagram. The second bar graph shows whether each reel I see uses hashtags or not. The third graph is a scatter plot and it shows a correlation between the number of reposts on a reel and the number of comments.


```{r}
library(tidyverse)

#opening and renaming data
data_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vR7j-BXhJrAlIE5bCH14ubr5N2NN4qFbpSPwQFeQhodldStVI5Tgl_S-US9jawDeKKIc8TAktsAYT_P/pub?output=csv"
logged_data <- read.csv(data_url)
latest_data <- rename(logged_data,
                      reposts = 2,
                      comments = 3,
                      categories = 4,
                      hashtags = 5,
                      sound = 6) %>%
  
view(latest_data)

# Splitting category data into multiple rows for graph
latest_data_split <- latest_data %>%
  mutate(categories = as.character(categories)) %>%
  separate_rows(categories, sep = ",\\s*") %>%          
  mutate(categories = tolower(categories))             

# Plotting graphs

category_bar <- ggplot(latest_data_split) +
  geom_bar(aes(y = categories)) +
  labs(title = "Number of reels in each category")
category_bar

hashtags_bar <- ggplot(latest_data) +
  geom_bar(aes(x = hashtags)) +
  labs(title = "Number of reels with hashtags")
hashtags_bar

reposts_comments_plot <- ggplot(data = latest_data,
                             aes(x = reposts,
                                 y = comments)) +
  geom_point(size = 2, shape = 23) + 
  geom_smooth(method ='lm', formula = y~x) +
  labs(title = "Correlation between reposts and comments",
       x = "reposts",
       y = "comments")
reposts_comments_plot

#finding the most common categories


#calculating percentage of reels with hashtags

hashtag_percentage <- (sum(tolower(trimws(latest_data$hashtags)) == "yes", na.rm = TRUE)/35)*100

#calculating average number of comments to average number of reposts
comments_reposts_ratio <- mean(latest_data$comments)/mean(latest_data$reposts)

#paste statements

paste("The percentage of reels with hashtags was",
      round(hashtag_percentage, 1), "%.")

paste("The average number of comments to reposts was", round(comments_reposts_ratio, 1))


```


